Project Protocol

### 2019-10-21 protocol.Rmd
procedures modified

As the survey is conducted through the Figure-Eight platform, IP Address Contributor ID, Trust Score and Channel(add link to Figure 8 details page ) will be provided. In addition to the experimental design and response variables:

- Plot type ( Hexagon / Geographic )
- Trend model ( Two hotspots / Multiple hotspots / spatial trend )
- Choice of plot in each line up
- Reason for choice of plot
- Time taken to answer
- Perceived difficulty of question

the survey of participants will provide this demographic information:

- Gender (female / male / other),
- Degree education level achieved (high school / bachelors / masters / doctorate / other),
- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
- Lived in Australia (Yes / No / other)

##	Data collection/gathering techniques: 
Data will be collected through survey distribution via a web application.
Participants will access the application via link from a Figure-Eight "job".

##	Impact of, and response to, missing data
If participants want to provide and "I don't know" answer they will be able to select this.
If there are more than 50% of questions that are incomplete we will remove this survey and consider this withdrawal.

>>>>

As the survey is conducted through the Figure-Eight platform, which will record IP Address of computer used to access the survey, Contributor ID, Trust Score and Channel. In addition, we will record the responses of participants:

- Choice of plot in each line up
- Reason for choice of plot
- Time taken to answer
- Perceived difficulty of question

and participants will be asked provide this demographic information:

- Gender (female / male / other),
- Degree education level achieved (high school / bachelors / masters / doctorate / other),
- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
- Lived at least for one year in Australia (Yes / No )

The experimental design variables, Plot Type, Trend Model and simulation number will also be saved for each display shown to participants.

##	Data collection/gathering techniques

Data will be collected through survey distribution via a web application.
Participants will access the application via a link from the Figure-Eight "job".

##	Impact of, and response to, missing data

Participants have the option to not respond to any question.

If there are 50% or more of unanswered survey questions (excluding demographic information) we will remove this participant's responses before data analysis.
